---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# livercells

<!-- badges: start -->
<!-- badges: end -->

livercells package can be used to deconvolute the cell composition from any liver tissue using its RNA-seq data. It can be helpful for to analyse the cell composition for samples related to various liver diseases and cancer. 

## Installation

You can install the livercells from [Bin-Chen-lab repository](https://github.com/Bin-Chen-Lab/livercells) with:

``` r
devtools::install('Bin-Chen-Lab/livercells')
```

## Usage



```{r usage}
library(livercells)
exp.matrix=read.csv("exp_data.csv", header = T, row.names = 1)
livercells(exp.matrix)
```

This function performed the cell enrichemnt for the liver tissue.

## Data input

The expression data should contains the normalized expression values with gene in rows and samples in columns. The rownames should be gene Symbols. livercells package uses the normalized expression value (TPM or FPKM value). The gene signatures are provided in the package, but if anyone wants to use their own signature they can do that. if anyone have control and disease dataset, they can combined all the samples in one matrix and use it.

## Contributors
livercells is developed by BinChen lab. Any questions or feedback can be addressed to Rama Shankar, PhD, ramashan@msu.edu or Bin Chen, PhD, PI, bin.chen@hc.msu.edu
